\documentclass[../main.tex]{subfiles}

\begin{document}

\section{Roles and Responsibilities Breakdown}

\noindent Overall, the codebase was equally worked upon by the entire team. Contributions are demonstrated in the commit history best, but the following outlines the main tasks each member worked on.

\noindent \textbf{Kutay:}
\begin{itemize}
    \itemsep-0.2em 
    \item Statistics calculators and UI panels: Created the framework, created and added all of the statistical views. Created the statistics controller to go through the different panels.
    \item Created pop-up on the map to view detailed information about location.
    \item Created the API that accesses the Postcode.io end-point to get detailed information about the location, such as region, borough, and constituency.
    \item Created the singleton class \verb|DataManager| to be the entry point to the pollution data.
    \item Started the colouring framework for the map pollution values.
\end{itemize}

\noindent \textbf{Anas:}
\begin{itemize}
    \itemsep0em 
    \item Pollution layer - rendering of pollution polygons onto the map, handling scaling, sizing, mapping squares onto spherical world-map and optimisation with LODs (Level Of Details)
    \item Pollution threshold system
    \item Improvements and small refactors in colour system and legend 
    \item Major refactors throughout the integration of UI and backend elements (model-view system)
\end{itemize}

\noindent \textbf{Matthias:}
\begin{itemize}
    \itemsep0em 
    \item Implemented Data Picker to dynamically select a data set according to the Pollutant and Year with the GUI Sidebar and ComboBox selectors
    \item Implemented Real-Time Air Quality Index API
    \item Updated Information Pop-Up to display more detailed information at a given data point
    \item Created About and Welcome Page GUIs 
\end{itemize}

\noindent \textbf{Chelsea:}{}
\begin{itemize}
    \itemsep0em 
    \item Collapsible legend pane
    \item Colourblind colour scheme
    \item Zoom Control Buttons - Zoom In/Out and Fullscreen
    \item Cat button to toggle side panel visibility
    \item Design/layouts of UI components (apart from statistics-related stuff)
\end{itemize}

\end{document}